Forecasting the United States 2024 Presidential Election

### 2024-11-03 paper/paper.qmd
fixed up results

Our model predicts that Harris has a 63.8% chance of winning the US presidential election. While Trump only has a 36.2% chance of winning. On average across the 1,000 simulations Harris wins 275.73 Electoral Votes, while Trump wins on average 259.27 votes.

```{r}
election_results %>%
  kable("html", caption = "Election Prediction Results") %>%
  kable_styling(
    "bordered",
    full_width = FALSE,
    position = "center"
  ) %>%
  add_header_above(c(" " = 1, "Candidates" = 2)) %>%
  row_spec(0, bold = TRUE) # Makes the header row bold

>>>>

Our model predicts that Harris has a 68.8% chance of winning the US presidential election. While Trump only has a 30.1% chance of winning. There is also a 1.1% chance of a tie On average across the 1,000 simulations Harris wins 279.21 Electoral Votes, while Trump wins on average 258.79 votes.

```{r}
election_results <- data.frame(
  Metric = c("Chance of Winning", "Average Electoral Votes"),
  Harris = c("68.8%", "279.21"),
  Trump = c("30.1%", "258.79"),
  stringsAsFactors = FALSE
)

election_results %>%
  kable("html", caption = "Election Prediction Results") %>%
  kable_styling(
    "bordered",
    full_width = FALSE,
    position = "center"
  ) %>%
  add_header_above(c(" " = 1, "Candidates" = 2)) %>%
  row_spec(0, bold = TRUE) # Makes the header row bold
